%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\name{Yang Wang} % Your name
\address{\\ 222 Escuela Ave, Mountain View, CA 94040 \\ (443) 538-4624 \\ wangyangtc@gmail.com} % Your address

\begin{document}


%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

\begin{rSubsection}{Facebook, Inc}{08/2013 - Present}{Senior Big Data Engineer}{Menlo Park, CA}{Designs and develops software frameworks and systems, data-driven web applications and services, and data processing pipelines to leverage Facebook big consumer and enterprise data for big business and engineering impact}
\item Built a data processing and exchange platform distributing Facebook conversation data to external analytics partners at scale
\item Developed a marketing analytical tool offering insight about the conversations people are having on Facebook.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{CBS Interactive}{09/2010 - 08/2013}{Software Engineer}{Boston, MA}{Designed and developed online optimization and recommendation services for all business units to improve website traffic and revenue using cutting-edge open source and big data technologies.}
\item Implemented an adaptive real-time content optimization platform to automatically promote content in a way that maximizes response rate using Beta-Binomial model.
\item Developed a high volume web service to capture, collect, organize, and serve comprehensive real-time data about content trends.
\item Built an A/B testing solution to help site owners ascertain which variation of a page produces the best improvement in the defined metrics.
\item Implemented an item based collaborative filtering recommendation system to deliver related content using association mining with various association metrics such as Confidence, Cosine, Normalized Mutual Information (NMI) etc, and agglomerative clustering model of search engine query log.
\item Built a data processing pipeline to extract tags and topics from raw documents of major websites and post tagged and indexed documents into Solr.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{OmniClaim}{06/2009 - 08/2010}{Software Engineer}{Woburn, MA}{Implemented and customized analytics to identify target medical claims for the nations largest insurance companies using Microsoft data solutions and business intelligence tools.}
\item Developed new stored procedures to detect potential overpaid claims.
\item Optimized the performance of existing queries using SQL Server Profiler and Database Engine Tuning Advisor.
\item Implemented ETL process to integrate data from various sources using SQL Server Integration Service.
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Languages & C++, Python, PHP, Java, SQL \\
Databases & MySQL, Hive, Presto, Vertica, Teradata \\
Deep Learning & Caffe2, TensorFlow \\
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}
\textbf{Tufts University}, Medford, MA \\
Master of Science, Computer Science, 2009 \\

\textbf{University of Science and Technology of China}, Hefei, China \\
Bachelor of Science, Physics, 2006 \\

\end{rSection}

%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
